### 2020-07-12 paper_dse_spb.Rmd
segundo commit

---
title: "'El efecto de la Desigualdad Socio-espacial en el Sentido de Pertenencia al Barrio: el caso de Santiago de Chile"
author: "Cristóbal Ortiz y Valentina Vásquez"
date: "11-07-2020"
output: html_document
---