### 2020-07-12 paper_dse_spb.Rmd
vamuos 2

---
title: "'El efecto de la Desigualdad Socio-espacial en el Sentido de Pertenencia al Barrio: el caso de Santiago de Chile"
author: "Cristóbal Ortiz y Valentina Vásquez"
date: "11-07-2020"
output: html_document
---
Abstract 
```{r}
install.packages("usethis")

library(usethis)
use_git_config(user.name = "Cristóbal Ortiz Vilches", user.email = "cristobal.ortiz.v@ug.uchile.cl")

#usethis::use_git_config(scope = "user")
```